### 2017-03-19 papers.tex
List 2017 paper reviews in build dependency list and master ToC
papers.tex: Update temporary TODOs
papers.tex: Cover all page numbers present in original submissions

% TODO: Add reviews
% TODO: Add Avalon paper
% TODO: Substitute in new PC message
% TODO: Spellcheck papers list
% TODO: Page numbers fixes?
% TODO: Add ice skating photos?
% TODO: Change title page font

% TODO: Update track "numbering" scheme
\addtrack{Bear track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{0cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

\addtrack{Mule track}{I'm Going to Use This!}
\addpaper
	{Who sorts the sorters?}
	{Alexander R.\ Frieder}
	{}
	{SIGBOVIK_2017_paper_39}
	{0cm}
	{}
\addpaper
	{Objectionability: A computational view of mathematical computation}
	{Cameron Wong and Dez Reed}
	{}
	{SIGBOVIK_2017_paper_18}
	{0cm}
	{}
\addpaper
	{Towards a well-defined and secure flirtation protocol}
	{Rowan Copley}
	{}
	{SIGBOVIK_2017_paper_72}
	{0cm}
	{}
\addpaper
	{A solution to the two-body problem}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_29}
	{0cm}
	{}

\addtrack{Magpie track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{0cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{0cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{0cm}
	{}

@@

\addtrack{Dog track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{0cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{0cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{0cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{0cm}
	{}

@@

\addtrack{Groundhog track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{0cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{0cm}
	{}

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{0cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{0cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{2M\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

@@

\addtrack{Moose track}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{0cm}
	{}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{0cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}

\addtrack{Raccoon track}{Talkin' Trash}
\addpaper
	{Garbage collection for heaps only a mother could love}
	{Your Parents}
	{}
	{SIGBOVIK_2017_paper_12}
	{0cm}
	{}
\addpaper
	{A new paradigm for robotic dust collection: Theorems, user studies, and a field study}
	{Rachel Holladay and Siddhartha S.\ Srinivasa}
	{}
	{SIGBOVIK_2017_paper_17}
	{0cm}
	{}

\addtrack{Cat track}{Work-\texorpdfstring{\sout{stealing}}\ saving}
\addpaper
	{The Zero-color Theorem: An optimal poster design algorithm}
	{Michael Coblenz}
	{}
	{SIGBOVIK_2017_paper_11}
	{0cm}
	{}
\addpaper
	{Cerebral genus: Dead duck or phoenix?}
	{Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2017_paper_70}
	{0cm}
	{}

>>>>

% TODO: Add any new reviews
% TODO: Substitute in new PC message
% TODO: Spellcheck papers list
% TODO: Page numbers fixes?
% TODO: Add ice skating photos?
% TODO: Change title page font

% TODO: Update track "numbering" scheme
\addtrack{Bear track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{3cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

\addtrack{Mule track}{I'm Going to Use This!}
\addpaper
	{Who sorts the sorters?}
	{Alexander R.\ Frieder}
	{}
	{SIGBOVIK_2017_paper_39}
	{0cm}
	{}
\addpaper
	{Objectionability: A computational view of mathematical computation}
	{Cameron Wong and Dez Reed}
	{}
	{SIGBOVIK_2017_paper_18}
	{1cm}
	{}
\addpaper
	{Towards a well-defined and secure flirtation protocol}
	{Rowan Copley}
	{}
	{SIGBOVIK_2017_paper_72}
	{2cm}
	{}
\addpaper
	{A solution to the two-body problem}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_29}
	{3cm}
	{}

\addtrack{Magpie track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{3cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{1cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{0cm}
	{}

@@

\addtrack{Dog track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{1cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{1cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{1cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{0cm}
	{}

@@

\addtrack{Groundhog track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{3cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{3cm}
	{}
\addreview{SIGBOVIK_2017_review-23}{0cm}

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{2M\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

@@

\addtrack{Moose track}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{1.85cm}
	{}
\addreview{SIGBOVIK_2017_review-91}{0cm}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-75}{0cm}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{3cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}

\addtrack{Raccoon track}{Talkin' Trash}
\addpaper
	{Garbage collection for heaps only a mother could love}
	{Your Parents}
	{}
	{SIGBOVIK_2017_paper_12}
	{1cm}
	{}
\addpaper
	{A new paradigm for robotic dust collection: Theorems, user studies, and a field study}
	{Rachel Holladay and Siddhartha S.\ Srinivasa}
	{}
	{SIGBOVIK_2017_paper_17}
	{0cm}
	{}

\addtrack{Cat track}{Work-\texorpdfstring{\sout{stealing}}\ saving}
\addpaper
	{The Zero-color Theorem: An optimal poster design algorithm}
	{Michael Coblenz}
	{}
	{SIGBOVIK_2017_paper_11}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-11}{0cm}
\addpaper
	{Cerebral genus: Dead duck or phoenix?}
	{Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2017_paper_70}
	{0cm}
	{}
